### 2012-04-18 docs/getting_started/getting_started.tex
updates

\maestro\ requires the \boxlib\ library to manage the grids and 
parallelization.  We also rely on the build system in \boxlib\ to
build a \maestro\ executable.  \boxlib can be obtained via {\tt
git}\footnote{{\tt git} is an open-source source code version control
system.  It is a standard part of any Linux distribution.  You may
need to use your system's package manager to install {\tt git} if it
is not already present} as:
\begin{verbatim}
git clone https://ccse.lbl.gov/pub/Downloads/BoxLib.git
\end{verbatim}

@@

This option specifies the Fortran compiler.  We will use {\tt gfortran}, which is
the preferred compiler for \maestro.  Specifying this compiler will automatically
pull in the compiler settings as specified in {\tt BOXLIB\_HOME/Tools/F\_mk/}.

@@

Each problem requires an input file.  The inputs file consists of
lines of the form {\em parameter = value}, where {\em parameter} is
one of the many runtime parameters \maestro\ knows, and {\em value}
overrides the default value for that parameter.  For the {\tt test2}
problem, we will use the inputs file {\tt inputs\_2d}.  An overview of
some of the more common runtime parameters is given
in \S~\ref{sec:gettingstarted:runtime}, and a full list of
all \maestro\ runtime parameters and their default values is given in
Chapter~\ref{ch:runtimeparameters}.

@@

By default, the plotfiles will be named {\tt plt}{\em nnnnn}, where
the number {\em nnnnn} is the timestep number when the file was
outputted.  Similarly, the checkpoints are named {\tt chk}{\em
nnnnn}.  \boxlib\ plotfiles and checkpoints are actually directories,
with the data stored in sub-directories grouped by refinement level.
Details of the simulation (build information, number of processors
used, output date, output directory, runtime parameter values, ...)
are stored in the {\tt job\_info} file in each plotfile directory.

@@

\amrvis\ uses the {\tt Motif} library for defining the GUI.  On a Linux 
system, you may need to install the {\tt lesstif} package and any
related development packages (e.g.\ {\tt lesstif-devel}).  Depending
on your Linux system, you may also need to install {\tt libXpm} 
and related development packages (e.g.\ {\tt libXpm-devel}).

%need to modify _f95_lib

library line

>>>>

\maestro\ requires the \boxlib\ library to manage the grids and 
parallelization.  We also rely on the build system in \boxlib\ to
build a \maestro\ executable.  \boxlib\ can be obtained via {\tt
git}\footnote{{\tt git} is an open-source source code version control
system.  It is a standard part of any Linux distribution.  You may
need to use your system's package manager to install {\tt git} if it
is not already present} as:
\begin{verbatim}
git clone https://ccse.lbl.gov/pub/Downloads/BoxLib.git
\end{verbatim}

@@

This option specifies the Fortran compiler.  We will use {\tt
gfortran}, which is the preferred compiler for \maestro.  Specifying
this compiler will automatically pull in the compiler settings as
specified in {\tt BOXLIB\_HOME/Tools/F\_mk/}.  (Alternate compiler
choices include {\tt Intel}, {\tt PGI}, {\tt PathScale}.)

@@

Each problem requires an input file.  The inputs file (a Fortran
namelist) consists of
lines of the form {\em parameter = value}, where {\em parameter} is
one of the many runtime parameters \maestro\ knows, and {\em value}
overrides the default value for that parameter.  For the {\tt test2}
problem, we will use the inputs file {\tt inputs\_2d}.  An overview of
some of the more common runtime parameters is given
in \S~\ref{sec:gettingstarted:runtime}, and a full list of
all \maestro\ runtime parameters and their default values is given in
Chapter~\ref{ch:runtimeparameters}.

@@

By default, the plotfiles will be named {\tt plt}{\em nnnnn}, where
the number {\em nnnnn} is the timestep number when the file was
outputted.  Similarly, the checkpoints are named {\tt chk}{\em
nnnnn}.  \boxlib\ plotfiles and checkpoints are actually directories,
with the data stored in sub-directories grouped by refinement level.
Details of the simulation (build information, number of processors
used, output date, output directory, runtime parameter values, ...)
are stored in the plaintext {\tt job\_info} file in each plotfile directory.

@@

\amrvis\ uses the {\tt Motif} library for defining the GUI.  On a Linux 
system, you may need to install the {\tt lesstif} package and any
related development packages (e.g.\ {\tt lesstif-devel}).  Depending
on your Linux system, you may also need to install {\tt libXpm} and
related development packages (e.g.\ {\tt libXpm-devel}).  Also, in
{\tt BoxLib/Tools/C\_mk/Make.defs}, the Fortran libraries are
explictly linked in by asking {\tt gfortran} for the location of {\tt
libgfortran.a}.  You may need to explicitly install the static
libraries for {\tt gfortran} (i.e.\ {\tt libgfortran-static}), or
change the library line to query for the shared-object version {\tt
libgfortran.so}.

Further details on the C++ \boxlib\ build system used by \amrvis\
can be found in the \boxlib\ documentation.
